RationalGRL: A Framework for Argumentation and Goal Modeling

### 2019-02-04 Response to reviewers3.txt

We thank the reviewers for their work.

Reviewer 1 again proposes to accept the paper. Reviewer 2 recommends rejection. The editor proposes that we perform major revisions.

We have worked hard to improve the paper since the first submission. We propose a new framework, inserting argument schemes and formal argument semantics into goal modelling in a way that hasn't been done before. We formally ground this framework in a logical framework for argumentation that has been accepted as a de-facto standard for non-monotonic argumentation inside and outside the field of AI. We give a simple development process, and a fully-working tool. We have further performed an extensive coding analysis, plus a modest expert survey.

@@

======= COMMENT #6
In this context, let me also say a few words on the "Case Study":
-       It cannot be taken as evidence for the approach, since studying recorded design sessions (without goal modeling) is reported in this paper as the basis for creating the argumentation structures in the first place. And this was done by the authors themselves based on their intuition.
-       Actually, this is not really a case study in the sense used in scientific literature. As a matter of fact, it also does not contain lessons learned.
======= REPLY #6
We agree that "case study" is perhaps not the most opportune name. It is, if you want to be precise, a qualitative empirical coding study with a priori coding. We have changed the text in the paper to reflect this.

======= COMMENT #7
In addition, I am still not convinced by the argument for dismissing formal reasoning in propositional logic. After all, it is not theoretically difficult and tools exist. So, what is the point of presenting special-purpose "algorithms" here?
======= REPLY #7
The argumentation formalism we propose is a non-monotonic logic, that is, earlier results might not be true when new information is added. Formal reasoning in propositional logic, taking the semantics of classical logic, is inherently monotonic: you can add propositions (arguments, goals), but these will never change the status (true/false) of existing propositions. Formal reasoning in propositional logic would be possible using, for instance, SAT solvers, but this would require a monotonic logic. Theorem provers for non-monotonic logics are significantly more complex, and not the focus of our research.

======= COMMENT #8
Finally, "defending" a binary framework simply by a reference is insufficient. Since the authors propose such a framework, they need to clearly point out its limitations in this regard.
======= REPLY #8
We already included some discussion in the previous revision. We have included an extra sentence on why we think numerical, more fine-grained frameworks are not very suitable. Furthermore, note that the framework is not "binary" in the sense that arguments can only be true or false (as in classical logic): arguments which are at one point considered defeated or overruled can later become justified again if new arguments are added.

======= COMMENT #9
From an editorial perspective, a careful proof reading of grammar would be necessary.
======= REPLY #9
We have revised our entire article in detail and corrected a large number of grammatical mistakes.

### 2019-02-04 casestudy.tex
small sentence & ref coding

Recall that \textbf{Requirement 1} of our RationalGRL framework is that the argumentation techniques should be close to the actual discussions of stakeholders or designers in the early requirements engineering phase. To get a sense of such discussions, we performed a coding analysis to examine which types of discourse are used during discussions of system requirements, and how these discourse types can be captured as argument schemes and critical questions. We manually coded transcripts of such discussions using a list of argument schemes and critical questions based on GRL and PRAS. In this section, we present our coding analysis. All original transcripts, codings, and models are available in our online repository, which can be found at:

>>>>

Recall that \textbf{Requirement 1} of our RationalGRL framework is that the argumentation techniques should be close to the actual discussions of stakeholders or designers in the early requirements engineering phase. To get a sense of such discussions, we performed a coding analysis to examine which types of discourse are used during discussions of system requirements, and how these discourse types can be captured as argument schemes and critical questions \cite{saldana2015coding}. The type of coding we performed is \emph{a priori coding}: we manually coded transcripts of such discussions using a pre-existing list of argument schemes and critical questions based on GRL and PRAS. In this section, we present our coding analysis. All original transcripts, codings, and models are available in our online repository, which can be found at:
